Followers Are Not Enough: A Question-Oriented Approach to Community Detection in Online Social Networks

### 2014-08-25 paper-for_arxiv/conclusions.tex
Added modifications after pass through paper.
random edits

In this study, we have demonstrated that the communities observed in online social networks are highly question-dependent. The questions posed about a network \emph{a priori} have a strong impact on the communities observed.  Moreover, using different definitions of \emph{community} reveal different and interesting relationships between users. More importantly, we have shown that these different views of the network are not revealed by using the structural network or any one weighting scheme alone. By varying the questions we asked about the network and then deriving weighting schema to answer each question, we found that community structure differed across community types on both the macro (e.g. number of communities and their size distribution) and micro (e.g. specific memberships, comemberships) scale in interesting ways.

@@

To verify the validity of these communities we demonstrated that boundaries between communities represent meaningful internal/external divisions. In particular, conversations (e.g. retweets and mentions) and topics (e.g. hashtags) tended to be most highly concentrated within communities. We found this to be the case even when the communities were defined by a different criterion from the edge weights under study.

>>>>

In this study, we have demonstrated that the communities observed in online social networks are highly question-dependent. The questions posed about a network \emph{a priori} have a strong impact on the communities observed.  Moreover, using different definitions of community reveal different and interesting relationships between users. More importantly, we have shown that these different views of the network are not revealed by using the structural network or any one weighting scheme alone. By varying the questions we asked about the network and then deriving weighting schema to answer each question, we found that community structure differed across community types on both the macro ({\it e.g.,} number of communities and their size distribution) and micro ({\it e.g.,} specific memberships, comemberships) scale in interesting ways.

@@

To verify the validity of these communities we demonstrated that boundaries between communities represent meaningful internal/external divisions. In particular, conversations ({\it e.g.,} retweets and mentions) and topics ({\it e.g.,} hashtags) tended to be most highly concentrated within communities. We found this to be the case even when the communities were defined by a different criterion from the edge weights under study.

### 2014-08-25 paper-for_arxiv/results.tex
random edits

\begin{figure}[ht]
  \centering
%\includegraphics[width=0.50\textwidth]{comm_sizes_ecdf_loglog.pdf}
\includegraphics[width=1\textwidth]{cdf_comm_sizes.pdf}
\caption{The proportion of communities greater than $s$ in size, across the different community types. Note the logarithmic scale on the horizontal and vertical axes.}
\label{Fig-community_size_distribution}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \begin{tabu}{cl}
    \toprule
    Normalized Mutual Information & Community Types \\
    \midrule
    \multirow{8}[8]{*}{\includegraphics[width=0.50\textwidth]{nmi_singletons.pdf}}&0---Structural \bigstrut\\
    &1-6---Activity-Based with Lags 1-6\bigstrut\\
    %&2---Activity-Based with Lag 2\bigstrut\\
    %&3---Activity-Based with Lag 3\bigstrut\\
    %&4---Activity-Based with Lag 4\bigstrut\\
    %&5---Activity-Based with Lag 5\bigstrut\\
    %&6---Activity-Based with Lag 6\bigstrut\\
    &7---Topic-Based \bigstrut\\
    &8---Interaction-Based with Mentions\bigstrut\\
    &9---Interaction-Based with Retweets\bigstrut\\
    &10---Interaction-Based with both \bigstrut\\
    &\,\,\,\,\,\,\,\,\,\,\,\,\,\,Mentions and Retweets\bigstrut\\
    &\bigstrut\\
    \bottomrule
\end{tabu}
\caption{The normalized mutual information between the coverings inferred from the different community types. 
%Community type 0 corresponds to the structural communities, community types 1 through 6 correspond to the activity-based communities with lag 1 through 6 transfer entropies, community type 7 corresponds to the topic-based communities, and community types 8, 9, and 10 correspond to the interaction-based communities using mentions, retweets, and both mentions and retweets. 
Values of normalized mutual information close to 1 indicate similarity in the community structure, while values close to 0 indicate dissimilarity. The normalized mutual information is computed with singletons and orphan nodes included.}
\label{Fig-compare_coverings}
\end{figure}

@@

\begin{figure}[!h]
	\centering
	\includegraphics[width=0.8\textwidth]{edge-types.pdf}
	\caption{A schematic of how, given a covering, the edges of the network can be partitioned using (\ref{Eqn-edge_types}) into inter-edges, intra-edges, and mixed-edges. Inter-edges (red dashed) cross community boundaries. Intra-edges (blue solid) remain inside community boundaries. Mixed-edges (purple dotted) both remain in and cross community boundaries due to overlap in community membership. Each column corresponds to the same collection of weights, but partitioned using a different covering. Each row corresponds to the same covering, but for the different weights.}
	\label{Fig-edge_types}
\end{figure}

@@

Each community type (Structural, Activity-based, Topic-based, Interaction-based) induces a different partition of the edges, and each edge type (Transfer Entropy, Hashtag, Mention-Retweet) induces a different distribution of weights. That is, let $W_{u \to f}$ be the weight on an edge $E_{u \to f}$ chosen uniformly at random from the network, and compute
\begin{align}
	P(W_{u \to f} \leq w_{u \to f} | T(E_{u \to f}) = t),
\end{align}
the empirical distribution over the edge weights conditioned on the edge type $t$ being one of inter, intra, and mixed. For meaningful community structure, we expect the distribution of edge weights to differ with the edge type $t$. If the community structure were arbitrary, the edge weights would be independent of the edge type, and all three conditional distributions would be identical.
The densities associated with these distributions are shown in Figure~\ref{Fig-distributions_by_types}.
\begin{figure}[!h]
	\centering
	\includegraphics[width=1\textwidth]{densities-edges.pdf}
	\caption{The density of edge weights for different community types (rows) and weight types (columns). The red,  blue, and purple values below each collection of densities indicate the median of weight on intra-, inter-, and mixed-edges, respectively.}
	\label{Fig-distributions_by_types}
\end{figure}

>>>>

\begin{figure}[ht]
  \centering
%\includegraphics[width=0.50\textwidth]{comm_sizes_ecdf_loglog.pdf}
\includegraphics[width=1\textwidth]{cdf_comm_sizes}
\caption{The proportion of communities greater than $s$ in size, across the different community types. Note the logarithmic scale on the horizontal and vertical axes.}
\label{Fig-community_size_distribution}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \begin{tabu}{cl}
    \toprule
    Normalized Mutual Information & Community Types \\
    \midrule
    \multirow{8}[8]{*}{\includegraphics[width=0.50\textwidth]{nmi_singletons}}&0---Structural \bigstrut\\
    &1-6---Activity-Based with Lags 1-6\bigstrut\\
    %&2---Activity-Based with Lag 2\bigstrut\\
    %&3---Activity-Based with Lag 3\bigstrut\\
    %&4---Activity-Based with Lag 4\bigstrut\\
    %&5---Activity-Based with Lag 5\bigstrut\\
    %&6---Activity-Based with Lag 6\bigstrut\\
    &7---Topic-Based \bigstrut\\
    &8---Interaction-Based with Mentions\bigstrut\\
    &9---Interaction-Based with Retweets\bigstrut\\
    &10---Interaction-Based with both \bigstrut\\
    &\,\,\,\,\,\,\,\,\,\,\,\,\,\,Mentions and Retweets\bigstrut\\
    &\bigstrut\\
    \bottomrule
\end{tabu}
\caption{The normalized mutual information between the coverings inferred from the different community types. 
%Community type 0 corresponds to the structural communities, community types 1 through 6 correspond to the activity-based communities with lag 1 through 6 transfer entropies, community type 7 corresponds to the topic-based communities, and community types 8, 9, and 10 correspond to the interaction-based communities using mentions, retweets, and both mentions and retweets. 
Values of normalized mutual information close to 1 indicate similarity in the community structure, while values close to 0 indicate dissimilarity. The normalized mutual information is computed with singletons and orphan nodes included.}
\label{Fig-compare_coverings}
\end{figure}

@@

\begin{figure}[!h]
	\centering
	\includegraphics[width=0.8\textwidth]{edge-types}
	\caption{A schematic of how, given a covering, the edges of the network can be partitioned using (\ref{Eqn-edge_types}) into inter-edges, intra-edges, and mixed-edges. Inter-edges (red dashed) cross community boundaries. Intra-edges (blue solid) remain inside community boundaries. Mixed-edges (purple dotted) both remain in and cross community boundaries due to overlap in community membership. Each column corresponds to the same collection of weights, but partitioned using a different covering. Each row corresponds to the same covering, but for the different weights.}
	\label{Fig-edge_types}
\end{figure}

@@

Each community type (Structural, Activity-based, Topic-based, Interaction-based) induces a different partition of the edges, and each edge type (Transfer Entropy, Hashtag, Mention-Retweet) induces a different distribution of weights. That is, let $W_{u \to f}$ be the weight on an edge $E_{u \to f}$ chosen uniformly at random from the network, and compute
\begin{align}
	P(W_{u \to f} \leq w_{u \to f} | T(E_{u \to f}) = t),
\end{align}
the empirical distribution over the edge weights conditioned on the edge type $t$ being one of inter, intra, and mixed. For meaningful community structure, we expect the distribution of edge weights to differ with the edge type $t$. If the community structure were arbitrary, the edge weights would be independent of the edge type, and all three conditional distributions would be identical.
The densities associated with these distributions are shown in Figure~\ref{Fig-distributions_by_types}.
\begin{figure}[!h]
	\centering
	\includegraphics[width=1\textwidth]{densities-edges}
	\caption{The density of edge weights for different community types (rows) and weight types (columns). The red,  blue, and purple values below each collection of densities indicate the median of weight on intra-, inter-, and mixed-edges, respectively.}
	\label{Fig-distributions_by_types}
\end{figure}
